Cybercrime and Online Video Games

### 2019-12-13 paper/paper.tex
Update paper.tex

% \begin{figure}
% \centering
% \begin{subfigure}{.5\textwidth}
% 	\centering
% 	\includegraphics[width = .4\linewidth]{ThreadCount}
% 	\caption{Thread Count}
% 	\label{fig:thread count}
% \end{subfigure}
% \begin{subfigure}{.5\textwidth}
% 	\centering
% 	\includegraphics[width=.4\linewidth]{Comment Count}
% 	\caption{Comment Count}
% 	\label{fig:comment count}
% \end{subfigure}
% \caption{Thread and Comment Pie Charts}
% \label{fig:thread and comment charts}
% \end{figure}

@@

\subsubsection{Jombah}
Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and [NUMBER] comments. He still passes the threshold for being a key player but the reason he is being focused on is due to his product. Jombah sells Fortnite accounts which is one of the crimewares we are focusing on. Jombah’s products are “premium” accounts which he appears to sell for a relatively cheap price as compared to other sellers though unlike some other sellers he does not offer custom accounts that a buyer can specify. Jombah is also a decently active user on hackerforum.net though not as active as Wyattz or as well liked by his customers. Jombah’s relevance lies not with his stellar service but with the product he provides.

>>>>

% \begin{figure}
% \centering
% \begin{subfigure}{.5\textwidth}
% 	\centering
% 	\includegraphics[width = .4\linewidth]{Thread Count}
% 	\caption{Thread Count}
% \end{subfigure}
% \begin{subfigure}{.5\textwidth}
% 	\centering
% 	\includegraphics[width=.4\linewidth]{Comment Count}
% 	\caption{Comment Count}
% \end{subfigure}
% \caption{Thread and Comment Pie Charts}
% \label{fig:thread and comment charts}
% \end{figure}

@@

\subsubsection{Jombah}
Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and 43 comments. He still passes the threshold for being a key player but the reason he is being focused on is due to his product. Jombah sells Fortnite accounts which is one of the crimewares we are focusing on. Jombah’s products are “premium” accounts which he appears to sell for a relatively cheap price as compared to other sellers though unlike some other sellers he does not offer custom accounts that a buyer can specify. Jombah is also a decently active user on hackerforum.net though not as active as Wyattz or as well liked by his customers. Jombah’s relevance lies not with his stellar service but with the product he provides.
